Supporting Information

### 2017-02-10 code/rmarkdown/supporting-information.Rmd
assorted changes to ms

Moderately-sized conservation planning problems often include several thousand planning units. It is currently not be feasible to solve this problem when considering all possible failure scenarios. As a consequence, the $R$ variable can be any $1 \leq R \leq J-1$. For instance, when $R=3$ only 2 backup levels are considered in addition to the final backup level. Cui et al. [-@r16] found that $R=5$ yields similar solutions to $R >> 5$. However, in most cases the decision maker will likely be limited to $R=1$ to obtain prioritizations in a feasible amount of time.

@@

We conducted a benchmark analysis to understand how much time would be required to solve different sized conservation planning problems. Additionally, we also aimed to understand how the time required to solve a problem varied depending on which formulation was used (unreliable or reliable), and if fragmentation constraints were used.

@@

We generated simulated data sets conservation planning problems using varying number of features `r paste(benchmark.params.LST$number.of.features, collapse=',')` and planning units (paste(benchmark.params.LST$number.of.planning.units, collapse=',')). For a given number of planning units and features, the data was simulated using the following steps. The planning units were simulated as squares that were arranged in a grid or near-grid like fashion. The units' costs were set to one. The spatial distribution of features were generated using binary spatially autocorrelated random fields [using the \texttt{RandomFields R} package; @rXXX]. If features were associated with less than two occupied planning units, these features were set to occupy two randomly selected planning units. All occupied planning units were set to have a probability of occupancy of `r benchmark.params.LST[[MODE]]$occupancy.probability`. Similar to the simulated data sets used in the main text, a geographic attribute space was used for each feature. The features' demand points were set as the centroids of the planning units that they occupied, and were weighted by the units' probability of occupancy. All problems used amount-based targets of `r benchmark.params.LST[[MODE]]$amount.target*100` % and space-based targets of `r benchmark.params.LST[[MODE]]$space.target*100`

We solved each conservation planning data set using the unreliable and reliable problem formulations (using default failure distance and level parameter) using no boundary length modifer, and using a boundary length modifier of `r max(benchmark.params.LST[[MODE]]$blm)`. To assess variation in solve times, we generated and solved `r benchmark.params.LST[[MODE]]$replicates` random data sets per combination of number of features and planning units. All conservation planning problems were solved to within `r general.params.LST[[MODE]]$MIPGap * 100` % of optimality using Gurobi (version 7.0.0) and a an Intel(R) Xeon(R) CPU E5-2630 (version 3; 2.40 GHz). To provide comparable estimates for the typical user, problems were solved using `r as.english(general.params.LST[[MODE]]$threads)` threads.

## RESULTS

@@

>>>>

Conservation planning problems often use more than several hundred planning units. It is currently not be feasible to solve this problem when considering all possible failure scenarios within a reasonable amount of time (see Appendix S2). As a consequence, the $R$ variable can be any $1 \leq R \leq J-1$. For instance, when $R=3$ only 2 backup levels are considered in addition to the final backup level. Cui _et al._ [-@r16] found that $R=5$ yields similar solutions to $R >> 5$. However, in most cases the decision maker will likely be limited to $R=1$ to obtain prioritizations in a feasible amount of time.

@@

We conducted a benchmark analysis to understand how much time would be required to build and solve different sized conservation planning problems. Additionally, we also aimed to understand how the time required to execute a problem varied depending on which formulation was used (unreliable or reliable), and if fragmentation constraints were used.

@@

We generated simulated conservation planning data sets using varying number of features `r paste(benchmark.params.LST$number.of.features, collapse=',')` and planning units (paste(benchmark.params.LST$number.of.planning.units, collapse=',')). For a given number of planning units and features, the data was simulated using the following steps. First, the planning units were simulated as squares that were arranged in a grid. All planning unit costs were set to one. The spatial distribution of features were generated using binary, spatially autocorrelated random fields [using the \texttt{RandomFields R} package; @rXXX]. If features were associated with less than two occupied planning units, these features were set to occupy two randomly selected planning units. All occupied planning units were set to have a probability of occupancy of `r benchmark.params.LST[[MODE]]$occupancy.probability`. Similar to the simulated data sets used in the main text, a geographic attribute space was used for each feature. The features' demand points were set as the centroids of the planning units that they occupied, and were weighted by the units' probability of occupancy. All problems used amount-based targets of `r benchmark.params.LST[[MODE]]$amount.target*100` % and space-based targets of `r benchmark.params.LST[[MODE]]$space.target*100`

We solved each conservation planning data set using the unreliable and reliable problem formulations (using default failure distance and level parameter) using no boundary length modifer, and using a boundary length modifier of `r max(benchmark.params.LST[[MODE]]$blm)`. To assess variation in execution times, we generated and solved `r benchmark.params.LST[[MODE]]$replicates` random data sets per combination of number of features and planning units. All conservation planning problems were solved to within `r general.params.LST[[MODE]]$MIPGap * 100` % of optimality using Gurobi (version 7.0.0) on a system with 64 GB RAM and an Intel(R) Xeon(R) CPU (E5-2630 v3; 2.40 GHz). All problems were solved using a single thread.

## RESULTS AND DISCUSSION

The benchmark analysis revealed that moderately-sized conservation problems can be solved in a realtively short period of time (Figure 1). As predicted, problems were solved much quicker when using the unreliable formulation than when using the reliable formulation. Additionally, the solve times varied substiantially for different data sets with the same proporties (ie. number of features and planning units). This result suggests that it may difficult to estimate exactly how long a given problem will take to solve.

@@

We were not able to explore how long large-sized problems would take to solve because our computer system did not have enough memory. One method to reduce the problem size is to set a maximum distance between demand points and planning units such that demand points cannot be represented by planning units that that are too far away. This method could be applied using functions provided in the \texttt{raptr R} package. Future research could involve implementing more advanced methods to solve the optimization problem [eg. as described in @r16; @r15].

### 2017-02-10 code/rmarkdown/text.Rmd
assorted changes to ms

To understand and showcase the behavior of the unreliable problem, we conducted a simulation study and two case studies. These studies involved generating solutions using only amount targets to represent prioritizations generated using conventional methods (eg. \texttt{Marxan}), and solutions using amount and space targets using the unreliable formulation. By comparing these solutions, we can gauge the benefits of explicitly including space targets in reserve selection. All analyses were performed in \texttt{R} [version `r getRversion()`; @r192].

>>>>

To understand and showcase the behavior of the unreliable problem, we conducted a simulation study and two case studies. These studies involved generating solutions using only amount targets to represent prioritizations generated using conventional methods (eg. \texttt{Marxan}), and solutions using amount and space targets using the unreliable formulation. By comparing these solutions, we can gauge the benefits of explicitly including space targets in reserve selection. We have also conducted a benchmark analysis to estimate how long it would take to solve various sized problem (Appendix S2). All analyses were performed in \texttt{R} [version `r getRversion()`; @r192] and all optimization problems were solved to within `r general.params.LST[[MODE]]$MIPGap * 100` % of optimality.
